---
title: "Rcapture_Estimation"
author: "Max Eckert"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##SETUP
```{r}
packages <- c("dplyr", "Rcapture") 
suppressPackageStartupMessages(
  invisible(lapply(packages, library, character.only = TRUE))
)
```


### Generating Capture History from List of Matched Incidents

Taking a dataframe, which includes all three lists, to generate a capture history, in which 1 indicates capture and 0 non-capture. 
```{r}
master_df <- read.csv2("./data/master_df.csv")

capture_hist <- master_df %>%
  mutate(
    mmp = ifelse(!is.na(mmp_id), 1, 0),
    foia = ifelse(!is.na(foia_id), 1, 0),
    sdpcome = ifelse(!is.na(sd_pcome_id), 1, 0)
  ) %>%
  select(mmp, foia, sdpcome)

head(capture_hist,10)
```

Converting the result into a matrix, which is then fed into the algorithm.

```{r}
capture_hist_matrix <- capture_hist %>% as.matrix()
```

##Descriptives about the Capture Hist
```{r}
all_three <- sum(rowSums(capture_hist_matrix == 1) == 3)

# Count the rows with 1 for each pairwise combination
pairwise_mmp_foia <- sum(rowSums(capture_hist_matrix[, c("mmp", "foia")] == 1) == 2)
pairwise_foia_sdpcome <- sum(rowSums(capture_hist_matrix[, c("foia", "sdpcome")] == 1) == 2)
pairwise_mmp_sdpcome <- sum(rowSums(capture_hist_matrix[, c("mmp", "sdpcome")] == 1) == 2)

# Output the results
print(paste("Rows with 1 for all three lists:", all_three))
print(paste("Rows with 1 for list 'mmp' and 'foia':", pairwise_mmp_foia))
print(paste("Rows with 1 for list 'foia' and 'sdpcome':", pairwise_foia_sdpcome))
print(paste("Rows with 1 for list 'mmp' and 'sdpcome':", pairwise_mmp_sdpcome))

# Create a new variable indicating rows with only one column having a value of 1
df <- df %>%
  mutate(unique_count = rowSums(. == 1) == 1)


# Count the number of rows where each column has a value of 1 while the other columns have 0
mmp_unique <- sum(capture_hist_matrix[, "mmp"] == 1 & capture_hist_matrix[, "foia"] == 0 & capture_hist_matrix[, "sdpcome"] == 0)
foia_unique <- sum(capture_hist_matrix[, "mmp"] == 0 & capture_hist_matrix[, "foia"] == 1 & capture_hist_matrix[, "sdpcome"] == 0)
sdpcome_unique <- sum(capture_hist_matrix[, "mmp"] == 0 & capture_hist_matrix[, "foia"] == 0 & capture_hist_matrix[, "sdpcome"] == 1)

# Print the result
print(c(mmp_unique, foia_unique, sdpcome_unique))


```


# Generate a closed population estimate

```{r}
descr <- descriptive(capture_hist_matrix, dfreq = FALSE)
descr
plot(descr)
```
There is only a very small overlap between all three lists (n=3), esp. since the MMP list is the smallest (n=22 units), the bigger overlap is between lists of the US Border Patrol FOIA request (n=339) and the Offices of the Medical Examiners (n=600). 

```{r}

```


## Running a Close Population Estimate

```{r}
cp <- closedp(capture_hist_matrix)
```

```{r}
models <- as.data.frame(cp$results)
models <- models %>% subset(infoFit == 0)
```
First thoughts: Standard Error moderate across models, with the exception of the bottom three. Column _infoFit_ contains a numerical code giving information about errors or warnings encountered; _0_ no error or warning occured while fitting the model; _1_ a warning indicating that the model fit is questionnable occured (algorithm did not converge, non-positive sigma estimate for a normal heterogeneous model or large asymptotic bias). No errors found. Very high variance for several models indicates a poor fit though. 

```{r}
cp_h <- closedpMS.t(capture_hist_matrix)
```

```{r}
M0_ci <- closedpCI.0(capture_hist_matrix, dfreq=FALSE, m="M0")
```

```{r}
Mt_ci <- closedpCI.t(capture_hist_matrix, dfreq=FALSE, m="Mt")
```

```{r}
Mthchao_ci <- closedpCI.t(capture_hist_matrix, dfreq=FALSE, m="Mth")
```

```{r}
Mh_ci <- closedpCI.t(capture_hist_matrix, dfreq=FALSE, m="Mh")
```


```{r}
descriptive(capture_hist_matrix, dfreq = FALSE)
```
Confidence Interval for Loglinear Model [1,2,3]
```{r}
abundance_estimation <- 1134.6
standard_error <- 46.8

# Degrees of freedom (df)
df <- 2  # From the model output

# Critical value for a 95% confidence interval
critical_value <- qt(0.975, df)  # 0.975 for a two-tailed test

# Calculate the margin of error
margin_of_error <- critical_value * standard_error

# Calculate the confidence interval
lower_bound <- abundance_estimation - margin_of_error
upper_bound <- abundance_estimation + margin_of_error

# Print the confidence interval
cat("95% Confidence Interval for Abundance Estimation:", "\n")
cat("Lower Bound:", lower_bound, "\n")
cat("Upper Bound:", upper_bound, "\n")
```

Confidence Interval for Loglinear Model [13,2]
```{r}
abundance_estimation <- 1114.9
standard_error <- 45.5 

# Degrees of freedom (df)
df <- 2  # From the model output

# Critical value for a 95% confidence interval
critical_value <- qt(0.975, df)  # 0.975 for a two-tailed test

# Calculate the margin of error
margin_of_error <- critical_value * standard_error

# Calculate the confidence interval
lower_bound <- abundance_estimation - margin_of_error
upper_bound <- abundance_estimation + margin_of_error

# Print the confidence interval
cat("95% Confidence Interval for Abundance Estimation:", "\n")
cat("Lower Bound:", lower_bound, "\n")
cat("Upper Bound:", upper_bound, "\n")
```

